Differentially Private Bayesian Inference

### 2018-03-29 main.tex
update laplace dilation
update  expomech proof
update exponential mech

\documentclass{article}
% \usepackage[utf8]{inputenc}
% \usepackage[english]{babel}
% Recommended, but optional, packages for figures and better typesetting:
\usepackage{mathtools,amssymb}
\usepackage{microtype}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{mathtools}
\usepackage{mdframed}
\usepackage{subfigure}
\usepackage{booktabs} % for professional tables
% hyperref makes hyperlinks in the resulting PDF.
% If your build breaks (sometimes temporarily if a hyperlink spans a page)
% please comment out the following usepackage line and replace
% \usepackage{icml2018} with \usepackage[nohyperref]{icml2018} above.
\usepackage{hyperref}
% \renewcommand\qedsymbol{$\blacksquare$}
% \theoremstyle{plain}
%   \newtheorem{thm}{Theorem}
% \theoremstyle{definition}
%   \newtheorem*{proof1}{Proof of Theorem \ref{Fermat}}
% Attempt to make hyperref and algorithmic work together better:
\newcommand{\theHalgorithm}{\arabic{algorithm}}
% \newenvironment{proofof}[1]{\par
%   \pushQED{\qed}%
%   \normalfont \topsep6\p@\@plus6\p@\relax
%   \trivlist
%   \item[\hskip\labelsep
%         \bfseries
%     Proof of #1\@addpunct{.}]\ignorespaces
% }{%
%   \popQED\endtrivlist\@endpefalse
% }
% Use the following line for the initial blind version submitted for review:
\usepackage{icml2018}
\input{macros}
% If accepted, instead use the following line for the camera-ready submission:
%\usepackage[accepted]{icml2018}

@@

\section{Dilation Property of Laplace Noise}
\label{sec_Dila}
\begin{proof}
We take 1-dimensional Laplace distribution, $h(z) = \frac{1}{2} e^{-|z|}$.
The dilation property is:
\begin{equation*}
Pr[z \in S] \leq e^{\frac{\epsilon}{2}} Pr[z \in e^{\lambda} S] + \frac{\delta}{2}
\end{equation*}
In this case, we have $\alpha = \frac{\epsilon}{2}$, $\beta = \frac{\epsilon}{2 \rho_{\delta/3}(|z|)}$ or $ \frac{\epsilon}{2 ln(2/\delta)}$. We have some prior knowledge that $|\lambda| \leq \beta$.

@@

@@

>>>>

\documentclass{article}
% \usepackage[utf8]{inputenc}
% \usepackage[english]{babel}
% Recommended, but optional, packages for figures and better typesetting:
\usepackage{mathtools,amssymb}
\usepackage{microtype}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{mathtools}
\usepackage{mdframed}
\usepackage{subfigure}
\usepackage{booktabs} % for professional tables
% hyperref makes hyperlinks in the resulting PDF.
% If your build breaks (sometimes temporarily if a hyperlink spans a page)
% please comment out the following usepackage line and replace
% \usepackage{icml2018} with \usepackage[nohyperref]{icml2018} above.
\usepackage{hyperref}
% \renewcommand\qedsymbol{$\blacksquare$}
% \theoremstyle{plain}
%   \newtheorem{thm}{Theorem}
% \theoremstyle{definition}
%   \newtheorem*{proof1}{Proof of Theorem \ref{Fermat}}
% Attempt to make hyperref and algorithmic work together better:
% \newenvironment{proofof}[1]{\par
%   \pushQED{\qed}%
%   \normalfont \topsep6\p@\@plus6\p@\relax
%   \trivlist
%   \item[\hskip\labelsep
%         \bfseries
%     Proof of #1\@addpunct{.}]\ignorespaces
% }{%
%   \popQED\endtrivlist\@endpefalse
% }
% Use the following line for the initial blind version submitted for review:
\usepackage{icml2018}
\input{macros}
% If accepted, instead use the following line for the camera-ready submission:
%\usepackage[accepted]{icml2018}

@@

\section{Smooth sensitivity}
\label{sec_smoo}

\subsection{Dilation Property of Laplace Noise}
\label{sec_Dila}
\begin{lem}
For 1-dimensional Laplace distribution, $h(z) = \frac{1}{2} e^{-|z|}$, $\alpha = \frac{\epsilon}{2}$, $\beta = \frac{\epsilon}{2 \rho_{\delta/3}(|z|)}$ or $ \frac{\epsilon}{2 ln(2/\delta)}$. We have some prior knowledge that $|\lambda| \leq \beta$, the $h$ has dilation property:
\begin{equation*}
Pr[z \in S] \leq e^{\frac{\epsilon}{2}} Pr[z \in e^{\lambda} S] + \frac{\delta}{2}
\end{equation*}
\end{lem}

\begin{proof}

@@

	i.e. the dilation property.

@@

\subsection{Sliding Property of Exponential Mechanism}
\begin{lem}
for any exponential mechanism $\mathcal{M}_E(x, u, \mathcal{R})$ $Pr[]$
\end{lem}
\begin{proof}
\end{proof}

\subsection{Dilation Property of Exponential Mechanism}
